Adaptative neighbouring methods applied to telephonic base stations

### 2024-08-22 article.tex
Res pot neigh

\begin{abstract}
    Nowadays, it is primordial for telecommunication companies to be able to determine if a user is moving. For that, it is necessary to understand the neighbouring relationships between the telephonic \acrlong{bs}s. This article aims at proposing and optimizing a method that adaptively detects these relationship between telephonic \acrlong{bs}s. This methods consists in multiple steps that can each be realised thanks to several methods that are compared : the $k$-NN method, the Delaunay triangulation or the Gabriel graph method are first used to create a first rough estimation of each point's neighbours. A filtering method is then applied in order to refine the neighbouring relationships that were found. This method is composed of several criteria that are succesfully being applied. These criterias are coming from previous works but were enhanced for better computational cost and results, and also to locally take into account the density of base station in the neighbours computation. The resulting method therefore gives a more accurate estimation of the neighbouring relationship than what was proposed before.
\end{abstract}
\section{Introduction}
    \IEEEPARstart{T}{he} field of telecommunication represents a gigantic mine of information, the smartphone penetration rate being 69\% in 2023 in the world, and 97\% in France. Therefore, the collected datas represent a big opportunity for telecommunication companies to predict their customers behaviour for internal or marketing purposes.

@@

        \subsubsection{\acrshort{dbscan}}
            The most intuitive method to use when trying to locate zones with high a high density of point is \acrshort{dbscan}. In fact, by applying the methods with the right parameters, these zones are detected in separate clusters and the rest is considered as noise. Two categories are therefore created : city (all the clusters) and countryside (the noise).

@@

    \subsection{Best potential neighbours}

>>>>

\begin{abstract}
    Nowadays, it is primordial for telecommunication companies to be able to determine if a user is moving. For that, it is necessary to understand the neighbouring relationships between the telephonic \acrlong{bs}s. This article aims at proposing and optimizing a method that adaptively detects these relationship between telephonic \acrlong{bs}s. This methods consists in multiple steps that can each be realised thanks to several methods that are compared: the $k$-NN method, the Delaunay triangulation or the Gabriel graph method are first used to create a first rough estimation of each point's neighbours. A filtering method is then applied in order to refine the neighbouring relationships that were found. This method is composed of several criteria that are succesfully being applied. These criterias are coming from previous works but were enhanced for better computational cost and results, and also to locally take into account the density of base station in the neighbours computation. The resulting method therefore gives a more accurate estimation of the neighbouring relationship than what was proposed before.
\end{abstract}
\section{Introduction}
    \IEEEPARstart{T}{he} field of telecommunication represents a gigantic mine of information, the smartphone penetration rate being 69\% in 2023 in the world, and 97\% in France. Therefore, the collected datas represent a big opportunity for telecommunication companies to predict their customers behaviour for internal or marketing purposes.

@@

        \subsubsection{\acrshort{dbscan}}
            The most intuitive method to use when trying to locate zones with high a high density of point is \acrshort{dbscan}. In fact, by applying the methods with the right parameters, these zones are detected in separate clusters and the rest is considered as noise. Two categories are therefore created: city (all the clusters) and countryside (the noise).

@@

    \subsection{Best potential neighbours}
        First of all, the $k$-NN method could have provided a solution to the fact that the Delaunay triangulation does not connect all the points but makes choices. However, to obtain interesting connections, we need to choose a relatively high $k$, greater than 10, which implies a large number of connections and therefore an increase in   computational cost. What's more, applying the criteria doesn't even produce convincing results.

        Secondly, the use of Gabriel's graph is not conclusive either. In fact, the use of this type of graph is not appropriate here because it will remove neighbourhood relationships that could have been retained.

        Finally, taking into account the above conclusions, the method used to construct the potential neighbourhood is the Delaunay triangulation.
